## Longitudinal Data
Growth analyses on assessment data require data that are linked to individual
students over time. Student growth percentile analyses require, at a minimum two,
and preferably three years of assessment data for analysis of student progress.
To this end it is necessary that a unique student identifier be available so
that student data records across years can be merged with one another and
subsequently examined. Because some records in the assessment data set contain
students with more than one test score in a content area in a given year, a
process to create unique student records in each content area by year combination
was required in order to carry out subsequent growth analyses. Furthermore,
student records may be invalidated for other reasons.

`r if (!is.null(params$valid.data.rule.general)) params$valid.data.rule.general`

`r if (params$eoct.tf) {cat("### End of Grade Student Records\n")}`

`r if (!is.null(params$valid.data.rule.eog)) params$valid.data.rule.eog`

Table `r tblNum(1)` shows the number of valid`r if (params$eoct.tf) {" EOG"}`
student records available for analysis after applying the data preparation
business rules. Note that this number does not represent the number of SGPs
produced, however, because students are required to have at least one prior
score available as well.

```{r, results="asis", echo=FALSE, N_table_EOG}
	n_tbl_eog <- table(sgp_object@Data[YEAR==params$sgp.year & CONTENT_AREA %in% params$GL_subjects & VALID_CASE=="VALID_CASE", GRADE, CONTENT_AREA])
	n_tbl_eog_B <- n_tbl_eog[match(params$GL_subjects, row.names(n_tbl_eog)) ,]
	n_tbl_eog_B <- cbind("Content Area"=sapply(params$GL_subjects, SGP::capwords, special.words=c("ELA", "US")), n_tbl_eog_B)
	n_tbl_eog_B <- prettyNum(n_tbl_eog_B, preserve.width = "individual", big.mark=",")
	n_tbl_eog_B[which(n_tbl_eog_B==0)] <- ""
	row.names(n_tbl_eog_B) <- NULL

  cat(dualTable(as.matrix(n_tbl_eog_B),
  	align=paste(rep("r", dim(n_tbl_eog_B)[2]), collapse=""),
		n.cgroup=c(1, dim(n_tbl_eog_B)[2]-1), cgroup=c("", "Grades"),
		caption=paste0("Number of Valid ", ifelse(params$eoct.tf, "EOG ", ""), "Student Records by Grade and Subject for ", params$year)))
```

`r if (params$eoct.tf) {cat("\n### End of Course Test Student Records\n")}`

`r if (!is.null(params$valid.data.rule.eoct)) params$valid.data.rule.eoct`

`r if (params$eoct.tf) {paste("Table", tblNum(1), "shows the total number of valid
EOC student records available for analysis after applying the general and EOC
specific business rules.")}`

```{r, results="asis", echo=FALSE, N_table_EOCT}
	if (params$eoct.tf) {
		n_tbl_EOC <- table(sgp_object@Data[YEAR == params$sgp.year & CONTENT_AREA %in% params$EOC_subjects & VALID_CASE=="VALID_CASE", GRADE, CONTENT_AREA])

		n_tbl_EOC_B <- n_tbl_EOC[match(params$EOC_subjects, row.names(n_tbl_EOC)) ,]
		n_tbl_EOC_B <- cbind("Content Area"=sapply(params$EOC_subjects, capwords, special.words=c("ELA", "II", "US")), "Valid Records" = n_tbl_EOC_B)
		n_tbl_EOC_B <- prettyNum(n_tbl_EOC_B, preserve.width = "individual",big.mark=",")
		row.names(n_tbl_EOC_B) <- NULL

	  cat(dualTable(as.matrix(n_tbl_EOCT_B), align=paste(rep("r", dim(n_tbl_EOCT_B)[2]), collapse=""),
			caption=paste("Total Number of Valid EOCT Student Records by Subject for", params$year), use.xtable = TRUE))
	}
```
