`r if (params$sgp.type != "SGP") {cat("\n###  Uncorrected model fit\n")}`
`r if (params$sgp.type != "SGP") {paste0("\n
Although the *official* SGPs used in ", params$state,"'s accountability system
incorporate ", ifelse(grepl("BASELINE", toupper(params$sgp.type)), "Baseline", ""),
ifelse(grepl("SIMEX", toupper(params$sgp.type)), "SIMEX measurement error correction", "calculations"),
" we provide uncorrected", ifelse(grepl("BASELINE", toupper(params$sgp.type)), ", cohort-referenced ", " "),
"SGP plots here as exemplars of cohort-referenced model fit, and to compare with",
ifelse(grepl("BASELINE", toupper(params$sgp.type)), " Baseline-referenced ", ""),
ifelse(grepl("SIMEX", toupper(params$sgp.type)), " SIMEX corrected and Ranked SIMEX ", ""),
"models that use the same student data in the subsequent sections.")}`

The model fit plots for `r ifelse(grepl("SIMEX", toupper(params$sgp.type)), "the unadjusted model results in ", "the cohort-referenced model results in ")`
all subjects are excellent with few exceptions (see Appendix A for all model fit
plots).  Figure `r getCounter("figure")+1` displays the
`r if (params$good.fit.example.grade != "EOCT") {paste0(params$good.fit.example.grade, "<sup>th</sup> grade")}`
`r params$good.fit.example.subject` model as an exemplar of model fit, and Figure
`r getCounter("figure")+2` is from `r if (params$misfit.example.grade != "EOCT") {paste(params$misfit.example.grade, "<sup>th</sup> grade")}`
`r misfit.example.subject`, which exemplifies the extent to which model misfit
is present in the `r params$state` SGP analyses. `r if (!is.null(params$good.fit.example.description)) params$good.fit.example.description`

```{r, results="asis", echo=FALSE}
	cohort.good_fit.plot <- grep(pattern="SIMEX|BASELINE", value=TRUE, invert=TRUE,
														   x=list.files(file.path("assets", "img", "Goodness_of_Fit", "good_fit"), recursive=TRUE, full.names = TRUE))
	cohort.good_fit.text <- ifelse(params$good.fit.example.grade != "EOCT", paste0(params$good.fit.example.grade, "<sup>th</sup> grade "), "")
	cohort.good_fit.text <- paste0(cohort.good_fit.text, capwords(params$good.fit.example.subject))
	tmp.caption <- paste0("Goodness of Fit Plot for", params$year, ifelse(params$sgp.type != "SGP", " ***Uncorrected*** ", ""),
												cohort.good_fit.text, ": Example of good model fit.")
	placeFigure(page.break= TRUE, pdf.width = 0.875, files = cohort.good_fit.plot, caption = tmp.caption)
```

Minor misfit in SGP models can be caused by several factors, such as the use of
a single prior in the model, relatively small cohort size and non-representative
or homogeneous cohorts (e.g., all advanced learner cohorts). These factors often
result in clustering of SGPs in some conditional distribution grid cells (dark
red cells adjacent to dark blue cells) because the norm group data does not
provide sufficient information to differentiate between students. `r if (!is.null(params$misfit.example.description)) params$misfit.example.description`

```{r, results="asis", echo=FALSE}
	cohort.misfit.plot <- grep(pattern="SIMEX|BASELINE", value=TRUE, invert=TRUE,
													   x=list.files(file.path("assets", "img", "Goodness_of_Fit", "misfit"), recursive=TRUE, full.names = TRUE))
	cohort.misfit.text <- ifelse(params$misfit.example.grade != "EOCT", paste0(params$misfit.example.grade, "<sup>th</sup> grade "), "")
	cohort.misfit.text <- paste0(cohort.misfit.text, capwords(params$misfit.example.subject))
	tmp.caption <- paste0("Goodness of Fit Plot for", params$year, ifelse(params$sgp.type != "SGP", " ***Uncorrected*** ", ""),
												cohort.misfit.text, ": Example of good model fit.")
	placeFigure(page.break= TRUE, files = cohort.misfit.plot, caption = tmp.caption)
```
